---
title: "data_summary"
author: "chengbo"
date: "2021/6/24"
output: pdf_document
---

```{r setup,echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r libraries,echo=FALSE,message=FALSE}
library(tidyverse)
library(kableExtra)

```
This is a report on happiness, where the indicator of happiness is represented by ladder_score.
The sample contains 149 countries, one of which has a very low ladder_score. In summary, the median of ladder_score is 5.534, and the average is 5.5. The standard deviation of the sample as a whole is 1.1, and the degree of dispersion of the sample is low.
In the second table, the sample is divided into ten groups according to the region. Sub-Saharan Africa has the largest number of samples, while North America and ANZ have the smallest number of samples. In contrast, Sub-Saharan Africa has the lowest happiness, while North America and ANZ have the highest happiness. The average happiness in most regions is in the range of 5-6. According to this table, North America and ANZ and Western Europe are the happiest regions.

```{r dataimport,echo=FALSE,message=FALSE,warning=FALSE}
happiness <- read_csv("world-happiness-report.csv")
happiness<-happiness%>%
  select(Regional_indicator,Ladder_score,Log_GDP_Capita,Social_support,Freedom_to_make_life_choices,Generosity,Perceptions_of_corruption,life_expectancy)

```
```{r datasummary,echo=FALSE,}
happiness %>%
  summarise(n=n(),Mean=round(mean(Ladder_score),digits=1), 
    St.Dev=round(sd(Ladder_score),digits=1), Min=min(Ladder_score), 
    Q1 = quantile(Ladder_score,0.25), Median=median(Ladder_score), 
    Q3 = quantile(Ladder_score,0.75), Max=max(Ladder_score)) %>%
  kable(caption = '\\label{tab:datasummary} Summary statistics on the Ladder Score of the countires.') %>%
  kable_styling(font_size = 10, latex_options = "hold_position")

```
```{r boxplot,echo=FALSE,fig.cap="\\label{fig:boxplot}The boxplot of Ladder Score"}
ggplot(data = happiness,mapping = aes(y=Ladder_score))+
  geom_boxplot(fill = "steelblue") +
  labs(y = "Ladder Score")
```



```{r regioncompare, echo=FALSE,fig.align = "center", fig.pos = "h",fig.cap="\\label{fig:region}Ladder Score in different regions"}
region_summary<-happiness%>%
  group_by(Regional_indicator)%>%
  summarise(mean=mean(Ladder_score),count=n())
region_summary
```






